Data Preparation

### 2019-01-10 Data Preparation.Rmd
move section up

### Course Catalogue
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

@@

### Course Manuals

@@

### Course Manual 
We create a dataframe from the Corpus:
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(Code = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

>>>>

### Extracting Text
(For this section we use:`corpus_catalogues` contains the pdfs of the `5` most recent course catalogues.)

@@

### Extracting Course Manual Text
We create a dataframe from the Corpus:
```{r d_manual}
d_manual <- tidy(corpus_manuals) %>%
  select(id, text) %>%
  mutate(Code = substring(id, 1, 7)) %>%
  select(-id) %>%
  rename(Manual = text)

@@

### Course Manual
